---
title: "Sean Conner resume"
author: Sean Conner
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: TRUE
    css:
      - custom_resume.css
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---

```{r setup, include = F}

library(tidyverse)

```


Aside
================================================================================

Contact Info {#contact}
--------------------------------------------------------------------------------
- <i class="fa fa-envelope"></i> scconner7@gmail.com
- <i class="fa fa-phone"></i> +1 601-490-5086
- <i class="fa fa-github"></i> [github.com/scconner7](https://github.com/scconner7)


<i class="fa fa-toolbox"></i> Languages and Tools {#languages}
--------------------------------------------------------------------------------
```{r, message=F, warning=F, echo = F, fig.height=14, fig.width=18}

create_skill_bar_data <-
  function(max_skill_level,
           skill_names,
           skill_levels) {
    skill_col <- function(skill_names, max_skill_level) {
      skill_names %>%
        map(~ rep(.x, max_skill_level)) %>%
        reduce(c)
    }
    
    df <-
      data.frame(skill = skill_col(skill_names, max_skill_level))
    
    max_level_col <- function(max_skill_level, skill_names) {
      rep(1:max_skill_level, length(skill_names))
    }
    
    df <- df %>%
      mutate(max_level = max_level_col(max_skill_level, skill_names))
    
    skill_level_col <- function(skill_levels, max_skill_level) {
      skill_levels %>%
        map(~ c(rep("Fill", .x), rep("Empty", max_skill_level - .x))) %>%
        reduce(c)
    }
    
    df <- df %>%
      mutate(skill_level = skill_level_col(skill_levels, max_skill_level))
    
    df
  }

skill_dots_data <-
  create_skill_bar_data(5,
                        c("SQL", "Python", "R", "Tableau", "Git", "Claude Code"),
                        c(5, 4, 5, 5, 4, 3))



skill_dots_data %>%
  ggplot() +
  geom_point(aes(
    x = max_level,
    y = fct_rev(fct_inorder(skill)),
    color = skill_level
  ), size = 40) +
  geom_hline(
    yintercept = c(seq(1.5, 6.5, by = 1)),
    color = "#ffe6e8",
    linetype = 2,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 1.5,
    yend = 1.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 2.5,
    yend = 2.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 3.5,
    yend = 3.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 4.5,
    yend = 4.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 5.5,
    yend = 5.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 6.5,
    yend = 6.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  coord_cartesian(xlim = c(1, 5), clip = "off") +
  scale_color_manual(values = c("light gray", "navy")) +
  theme(
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(
      margin = margin(0, 20, 0, 0),
      size = 65,
      color = "#737373",
      hjust = 0,
    ),
    plot.background = element_rect(fill = "#f5f8fc", color = "#f5f8fc"),
    panel.background = element_rect(fill = "#f5f8fc", color = "#f5f8fc"),
    legend.position = "none",
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "#f5f8fc")
  )

```


<i class="fa fa-certificate"></i> Certifications {#certs}
--------------------------------------------------------------------------------
- IBM Data Science Fundamentals Specialization ([verification link](https://www.credly.com/badges/5269971e-1d74-4273-8115-072d18b88e05?source=linked_in_profile))


<i class="fa fa-laptop"></i> Skills {#skills}
--------------------------------------------------------------------------------
<style>
div.flex-child {
flex: 0 1 auto;
background-color: #eff3ff;
border: 1px solid #d9d9d9;
border-radius: 5px;
box-sizing: border-box;
margin: 3px;
padding: 2px 5px 2px 5px;
max-height: 30px;
align-self: center;
}
</style>


<div style="display: flex; flex-wrap: wrap; max-width: 750px; padding: 3px; white-space: nowrap; align-items: center"; justify-content: center>

<div class="flex-child">
Data Visualization
</div>

<div class="flex-child">
Shiny
</div>

<div class="flex-child">
Writing
</div>

<div class="flex-child">
Statistical Analysis
</div>

<div class="flex-child">
Regression Modeling
</div>

<div class="flex-child">
Data Cleaning
</div>

<div class="flex-child">
R Markdown
</div>

<div class="flex-child">
Quarto
</div>

<div class="flex-child">
R tidyverse
</div>

<div class="flex-child">
Data Engineering
</div>

<div class="flex-child">
Business Intelligence
</div>

<div class="flex-child">
Survey Design
</div>

<div class="flex-child">
Microsoft Office
</div>

<div class="flex-child">
GitLab / GitHub
</div>

<div class="flex-child">
Time-Series
</div>

<div class="flex-child">
Atlassian Cloud
</div>

<div class="flex-child">
R Package Dev
</div>

<div class="flex-child">
Data Warehousing
</div>

<div class="flex-child">
Econometrics
</div>

<div class="flex-child">
Event-History Analysis
</div>

<div class="flex-child">
Machine Learning
</div>

<div class="flex-child">
dbt
</div>

<div class="flex-child">
dlt
</div>

<div class="flex-child">
Dagster
</div>

<div class="flex-child">
tSQLt
</div>

<div class="flex-child">
querychat
</div>

<div class="flex-child">
GitHub Copilot
</div>


</div>


<!-- Disclaimer {#disclaimer style="width: var(--sidebar-width); padding-left: var(--sidebar-horizontal-padding);"} -->
<!-- -------------------------------------------------------------------------------- -->
<!-- This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).<br></br> -->
<!-- Code available on my GitHub [**here**](https://github.com/scconner7/Pagedown-Resume).<br></br> -->
<!-- Last updated on `r Sys.Date()`. -->


Main
================================================================================

Sean Conner {#title}
--------------------------------------------------------------------------------
**Location:** Diamondhead, MS (USA)


Professional Experience {data-icon=laptop}
--------------------------------------------------------------------------------

### Senior Analytics Engineer

Green Mountain Technology

Remote full-time

Present - Aug. 2020

- Architected an event-driven webhook pipeline with rigorous data quality checks to validate payload completeness and enforce strict alignment with partner specifications.
- Engineered an end-to-end rate shop verification pipeline, transforming nested JSON into high-performance STAR schemas to map complex partner data to internal models.
- Orchestrate production data pipelines using Dagster, integrating diverse operational sources to drive enterprise analytics and accurate revenue forecasting.
- Championed enterprise adoption of dlt and dbt, maintaining ingestion frameworks for complex datasets including carrier service guides and contract pricing.
- Developed a specialized SQL schema and R Shiny CRUD app to standardize and validate strategic pricing parameters, enabling account teams to maintain critical analytics inputs.
- Core maintainer of the enterprise data warehouse and BI extracts, partnering across teams to ensure high availability and reliability for Tableau-driven insights.
- Automated EIA fuel price ingestion workflows, dynamically calculating fuel surcharge percentages based on carrier indexes and zip-to-zone mappings.
- Conducted strategic network optimizations and RFP evaluations for Fortune 100 clients, leveraging SQL and R to model large-scale parcel shipping data.
- Built automated reporting pipelines and parameterized models using R/RMarkdown, Shiny, and Tableau to deliver weekly and monthly executive-level insights.
- Led the operations-wide rollout of Git/GitLab, authoring technical documentation and conducting live training to standardize version control.
- Organized weekly engineering alignment summits to drive methodology standardization and cross-team knowledge sharing.

<!-- - Spearheaded a major partner integration by architecting an event-driven pipeline to ingest webhook data. Implemented rigorous data quality checks to validate payload completeness, enforce partner specifications, and ensure strict alignment with allowable enumerated values. -->
<!-- - Designed a comprehensive rate shop verification pipeline spanning from initial webhook ingest through to end-product dashboards. Engineered foundational STAR schemas by parsing, flattening, and transforming nested JSON payloads in SQL, seamlessly translating complex fields between partner and internal enterprise data models. -->
<!-- - Build, maintain, and orchestrate production-quality data asset pipelines using Dagster, connecting various operational sources to support enterprise analytics and accurate revenue forecasting. -->
<!-- - Championed the adoption and implementation of data load tool (dlt) and data build tool (dbt). Maintain ingestion frameworks to acquire and validate complex datasets, including major parcel carrier service guides, published list rates, and customer contract pricing parameters. -->
<!-- - Creater and lead maintainer / developer of a SQL schema optimized for loading customers' carrier contract and strategic what-if scenario pricing parameters in a standard location with built-in, robust data validations and an internal R Shiny CRUD app to facilitate account teams maintaining these critical inputs to internal analytics toolkit. -->
<!-- - Serve as a core maintainer of the enterprise data warehouse and BI data extracts (integrating with visualization tools like Tableau). Partner directly with analytics and engineering teams to ensure downstream data availability and reliability. -->
<!-- - Engineered automated workflows to ingest EIA published weekly fuel spot prices and dynamically calculate fuel surcharge percentages based on carrier-published indexes and zip-code-to-zone mappings. -->
<!-- - Conducted *ad hoc* strategic analyses of parcel shipping networks, such as request for proposal (RFP) evaluations and network optimizations for multiple Fortune 100 companies. -->
<!-- - Worked daily with large, complex datasets to create automated report pipelines, parameterized analytics models, and business intelligence dashboards using combinations of SQL, R / RMarkdown, Shiny, Excel, and Tableau. -->
<!-- - Summarized and presented *ad hoc*, weekly, and monthly analyses to audiences up to senior VP-level executives of Fortune 100 companies. -->
<!-- - Led operations-wide roll-out of Git & GitLab with self-authored tutorial documents and live demos. -->
<!-- - Organized weekly engineer alignment meetings to share methods and standardize work. -->


### Research Associate

MS State University - Stennis Institute of Government

Starkville, MS

Aug. 2020 - Aug. 2019

- Directed several high-impact research projects as PI/Co-PI, utilizing factor analysis and regression modeling to produce state-level program inventories and organizational reports.


### Graduate Research Assistant

MS State University - Stennis Institute of Government

Starkville, MS

Aug. 2019 - July 2017

- Developed Shiny web applications and survival analysis models to deliver stakeholder insights, presenting technical findings at national conferences.

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### MS State University

Ph.D - Public Policy and Administration

Starkville, MS

Present (Currently A.B.D. - anticipated graduation 2027)

GPA 4.00 / 4.00


### MS State University

Master of Public Policy and Administration (MPPA)

Starkville, MS

Aug. 2018 - Aug. 2016

GPA 4.00 / 4.00


### University of MS

Bachelor of Arts in Political Science

Oxford, MS

Aug. 2014 - Aug. 2010

GPA 3.34 / 4.00


Leadership & Awards {data-icon=medal data-concise=true}
--------------------------------------------------------------------------------

### Green Mountain Technology

Senior Solutions Engineer

Remote full-time

- Most Valuable Player (MVP) Award, nominated by peers and chosen by senior leadership as winner of 1 of only 2 such honors awarded company-wide each year (Winner in 2022 and nominated again every year since 2023).
- Discretionary Executive Leadership Bonus for Innovation recipient 3 consecutive years (2022-2024)


### MS State University

Student

Starkville, MS

- Outstanding Graduate Student (2018).
- Student Representative for MPPA program (September 2017 – May 2018).
- The Honor Society of Phi Kappa Phi (2017-2018).
- Best Graduate Student Paper / Presentation at MS Political Science Association Conference (2018).


### University of MS

Student

Oxford, MS

- Dean’s List (four semesters).
- Representative for University of MS at the National Model United Nations in NYC (2010).
- Pi Sigma Alpha, the Political Science Honors Society (2014).
- Provost Scholar (2010-2014).
- President for University of MS Model Senate (Fall 2013).
