---
title: "Sean Conner resume"
author: Sean Conner
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: TRUE
    css:
      - custom_resume.css
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---

```{r setup, include = F}

library(tidyverse)

```


Aside
================================================================================

Contact Info {#contact}
--------------------------------------------------------------------------------
- <i class="fa fa-envelope"></i> scconner7@gmail.com
- <i class="fa fa-phone"></i> +1 601-490-5086
- <i class="fa fa-linkedin"></i> [linkedin.com/in/scconner7](https://www.linkedin.com/in/scconner7)


<i class="fa fa-toolbox"></i> Languages and Tools {#languages}
--------------------------------------------------------------------------------
```{r, message=F, warning=F, echo = F, fig.height=14, fig.width=18}

create_skill_bar_data <-
  function(max_skill_level,
           skill_names,
           skill_levels) {
    skill_col <- function(skill_names, max_skill_level) {
      skill_names %>%
        map(~ rep(.x, max_skill_level)) %>%
        reduce(c)
    }
    
    df <-
      data.frame(skill = skill_col(skill_names, max_skill_level))
    
    max_level_col <- function(max_skill_level, skill_names) {
      rep(1:max_skill_level, length(skill_names))
    }
    
    df <- df %>%
      mutate(max_level = max_level_col(max_skill_level, skill_names))
    
    skill_level_col <- function(skill_levels, max_skill_level) {
      skill_levels %>%
        map(~ c(rep("Fill", .x), rep("Empty", max_skill_level - .x))) %>%
        reduce(c)
    }
    
    df <- df %>%
      mutate(skill_level = skill_level_col(skill_levels, max_skill_level))
    
    df
  }

skill_dots_data <-
  create_skill_bar_data(5,
                        c("SQL", "Python", "R", "Dagster", "Git", "Claude Code"),
                        c(5, 5, 5, 4, 5, 4))



skill_dots_data %>%
  ggplot() +
  geom_point(aes(
    x = max_level,
    y = fct_rev(fct_inorder(skill)),
    color = skill_level
  ), size = 40) +
  geom_hline(
    yintercept = c(seq(1.5, 6.5, by = 1)),
    color = "#ffe6e8",
    linetype = 2,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 1.5,
    yend = 1.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 2.5,
    yend = 2.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 3.5,
    yend = 3.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 4.5,
    yend = 4.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 5.5,
    yend = 5.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 6.5,
    yend = 6.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  coord_cartesian(xlim = c(1, 5), clip = "off") +
  scale_color_manual(values = c("light gray", "navy")) +
  theme(
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(
      margin = margin(0, 20, 0, 0),
      size = 65,
      color = "#737373",
      hjust = 0,
    ),
    plot.background = element_rect(fill = "#f5f8fc", color = "#f5f8fc"),
    panel.background = element_rect(fill = "#f5f8fc", color = "#f5f8fc"),
    legend.position = "none",
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "#f5f8fc")
  )

```


<i class="fa fa-certificate"></i> Certifications {#certs}
--------------------------------------------------------------------------------
- IBM Data Science Fundamentals Specialization ([verification link](https://www.credly.com/badges/5269971e-1d74-4273-8115-072d18b88e05?source=linked_in_profile))


<i class="fa fa-laptop"></i> Skills {#skills}
--------------------------------------------------------------------------------
<style>
div.flex-child {
flex: 0 1 auto;
background-color: #eff3ff;
border: 1px solid #d9d9d9;
border-radius: 5px;
box-sizing: border-box;
margin: 3px;
padding: 2px 5px 2px 5px;
max-height: 30px;
align-self: center;
}
</style>


<div style="display: flex; flex-wrap: wrap; max-width: 750px; padding: 3px; white-space: nowrap; align-items: center"; justify-content: center>

<div class="flex-child">
Data Engineering
</div>

<div class="flex-child">
Data Warehousing
</div>

<div class="flex-child">
ETL / ELT
</div>

<div class="flex-child">
dlt
</div>

<div class="flex-child">
dbt
</div>

<div class="flex-child">
Dagster
</div>

<div class="flex-child">
T-SQL
</div>

<div class="flex-child">
tSQLt
</div>

<div class="flex-child">
Polars
</div>

<div class="flex-child">
Shiny
</div>

<div class="flex-child">
Quarto
</div>

<div class="flex-child">
R Package Dev
</div>

<div class="flex-child">
R tidyverse
</div>

<div class="flex-child">
Machine Learning
</div>

<div class="flex-child">
Data Visualization
</div>

<div class="flex-child">
GitLab / GitHub
</div>

<div class="flex-child">
querychat
</div>


</div>


<!-- Disclaimer {#disclaimer style="width: var(--sidebar-width); padding-left: var(--sidebar-horizontal-padding);"} -->
<!-- -------------------------------------------------------------------------------- -->
<!-- This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).<br></br> -->
<!-- Code available on my GitHub [**here**](https://github.com/scconner7/Pagedown-Resume).<br></br> -->
<!-- Last updated on `r Sys.Date()`. -->


Main
================================================================================

Sean Conner {#title}
--------------------------------------------------------------------------------
**Location:** Diamondhead, MS (USA)

*Senior Analytics Engineer with six years productizing parcel-industry analytics — ships R packages, Python data pipelines, and reusable analytical frameworks at Fortune-100 scale. Public-policy researcher by training; engineer by trade.*


Professional Experience {data-icon=laptop}
--------------------------------------------------------------------------------

### Senior Analytics Engineer

Green Mountain Technology

Remote full-time

Aug. 2020 - Present

*Promoted: Solutions Engineer (2020) → Solutions Engineer II (2022) → Senior Analytics Engineer (2025).*

- Author and maintain two production R packages — a Shiny pricing-input application and a shared utility library — together comprising 100+ exported functions and 30+ Shiny modules powering rate management and analytics across the customer portfolio.
- Engineered a reusable package-consolidation analysis framework deployed across multiple Fortune-100 engagements; surfaces multi-million-dollar shipper savings opportunities by modeling tens of millions of package-level shipments against contractual rates with custom dim-weight, fuel, and bundling logic.
- Lead RFP and carrier-bid evaluations for Fortune-100 clients; built modular SQL frameworks modeling 100M+ package-level scenarios with custom surcharge, fuel, and incentive-tier logic to deliver negotiation-ready rate-card summaries.
- Designed and own a SQL schema for managing customer contract pricing parameters, with triggers, dynamic views, insert-routing, and validation UDFs enforcing data quality at write time.
- Authored a tSQLt unit-test suite (hundreds of tests) covering charge derivation and rating logic across the carrier-implementation matrix; protects nightly DW refreshes from regression.
- Engineered an event-driven webhook ingestion pipeline with payload-quality validation; transformed nested JSON into STAR-schema fact and dimension tables powering rate-shop verification.
- Built a natural-language SQL interface over the enterprise portfolio's shipping-charges data using Posit's querychat (Python / Shiny + Ibis); engineered a domain-grounded system prompt and structured data dictionary that lets non-technical stakeholders query the warehouse in plain English.
- Authored a small library of production Claude Code skills automating customer-contract parsing-and-loading (PDF / Excel / CSV → schema-aware SQL inserts), collapsing a multi-hour manual workflow to minutes.
- Architected a dlt → dbt → Dagster ELT platform spanning 100+ models and dozens of Python extraction assets; orchestrates daily refresh of customer-warehouse data feeding downstream analytics, forecasting, and BI extracts.
- Led operations-wide Git/GitLab rollout — authored canonical onboarding documentation, ran live training, and established branching and merge-request conventions adopted across analytics.

<!-- - Spearheaded a major partner integration by architecting an event-driven pipeline to ingest webhook data. Implemented rigorous data quality checks to validate payload completeness, enforce partner specifications, and ensure strict alignment with allowable enumerated values. -->
<!-- - Designed a comprehensive rate shop verification pipeline spanning from initial webhook ingest through to end-product dashboards. Engineered foundational STAR schemas by parsing, flattening, and transforming nested JSON payloads in SQL, seamlessly translating complex fields between partner and internal enterprise data models. -->
<!-- - Build, maintain, and orchestrate production-quality data asset pipelines using Dagster, connecting various operational sources to support enterprise analytics and accurate revenue forecasting. -->
<!-- - Championed the adoption and implementation of data load tool (dlt) and data build tool (dbt). Maintain ingestion frameworks to acquire and validate complex datasets, including major parcel carrier service guides, published list rates, and customer contract pricing parameters. -->
<!-- - Creater and lead maintainer / developer of a SQL schema optimized for loading customers' carrier contract and strategic what-if scenario pricing parameters in a standard location with built-in, robust data validations and an internal R Shiny CRUD app to facilitate account teams maintaining these critical inputs to internal analytics toolkit. -->
<!-- - Serve as a core maintainer of the enterprise data warehouse and BI data extracts (integrating with visualization tools like Tableau). Partner directly with analytics and engineering teams to ensure downstream data availability and reliability. -->
<!-- - Engineered automated workflows to ingest EIA published weekly fuel spot prices and dynamically calculate fuel surcharge percentages based on carrier-published indexes and zip-code-to-zone mappings. -->
<!-- - Conducted *ad hoc* strategic analyses of parcel shipping networks, such as request for proposal (RFP) evaluations and network optimizations for multiple Fortune 100 companies. -->
<!-- - Worked daily with large, complex datasets to create automated report pipelines, parameterized analytics models, and business intelligence dashboards using combinations of SQL, R / RMarkdown, Shiny, Excel, and Tableau. -->
<!-- - Summarized and presented *ad hoc*, weekly, and monthly analyses to audiences up to senior VP-level executives of Fortune 100 companies. -->
<!-- - Led operations-wide roll-out of Git & GitLab with self-authored tutorial documents and live demos. -->
<!-- - Organized weekly engineer alignment meetings to share methods and standardize work. -->


### Research Associate / Graduate Research Assistant

MS State University - Stennis Institute of Government

Starkville, MS

July 2017 - Aug. 2020

- Directed multiple research projects as PI/Co-PI, applying factor analysis and regression modeling to produce state-level program inventories and organizational reports.
- Built Shiny web applications and survival / event-history models to deliver stakeholder insights; presented technical findings at national conferences.

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### MS State University

Ph.D., Public Policy and Administration (A.B.D.)

Starkville, MS

Anticipated 2027

GPA 4.00 / 4.00


### MS State University

Master of Public Policy and Administration (MPPA)

Starkville, MS

Aug. 2016 - Aug. 2018

GPA 4.00 / 4.00


### University of MS

Bachelor of Arts in Political Science

Oxford, MS

Aug. 2010 - Aug. 2014

GPA 3.34 / 4.00


Leadership & Awards {data-icon=medal data-concise=true}
--------------------------------------------------------------------------------

### Green Mountain Technology

Senior Analytics Engineer

Remote full-time

- Most Valuable Player (MVP) Award — peer-nominated, leadership-selected; one of only two awarded company-wide annually. Recipient in 2022; nominated every year since.
- Discretionary Executive Leadership Bonus for Innovation — recipient three consecutive years (2022–2024).


### MS State University

Student

Starkville, MS

- Outstanding Graduate Student (2018).
- Student Representative for MPPA program (September 2017 – May 2018).
- The Honor Society of Phi Kappa Phi (2017-2018).
- Best Graduate Student Paper / Presentation at MS Political Science Association Conference (2018).


### University of MS

Student

Oxford, MS

- Dean's List (four semesters); Provost Scholar (2010–2014); Pi Sigma Alpha Honors Society (2014).
- President of UM Model Senate (Fall 2013); university delegate to National Model United Nations, NYC (2010).
